\documentclass[dvips,12pt]{article}

% Any percent sign marks a comment to the end of the line

% Every latex document starts with a documentclass declaration like this
% The option dvips allows for graphics, 12pt is the font size, and article
%   is the style

\usepackage[letterpaper, margin=1in]{geometry}

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage[pdftex]{xcolor}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{tabularx}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lfoot{2016 CFA Benefits of Collaboration 10565}
\rfoot{Page \thepage\ of \pageref{LastPage}}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0.5pt}

\newcommand{\unc}[1]
{ \delta #1 }

\newcommand{\uncsq}[1]
{ \left(\unc{#1}\right)^2 }

\newcommand{\uncratio}[1]
{ \left(\frac{\unc{#1}}{#1}\right) }

\newcommand{\uncratiosq}[1]
{ \uncratio{#1}^2 }

\newcommand{\uncvector}[1]
{ \left[ \begin{array}{c} #1 \\ \delta #1 \end{array} \right] }

\newcommand{\comment}[1]
{{\bfseries \color{red} #1}}

\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
                                   {-2.0ex \@plus -1ex \@minus -.2ex}%
                                   {2.3ex \@plus.2ex}%
                                   {\normalfont\bfseries}}% from \Large
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
                                     {-2.0ex\@plus -1ex \@minus -.2ex}%
                                     {1.5ex \@plus .2ex}%
                                     {\normalfont\bfseries}}% from \large
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
                                     {-2.0ex\@plus -1ex \@minus -.2ex}%
                                     {1.5ex \@plus .2ex}%
                                     {\normalfont\bfseries}}% from \normalsize
\makeatother


%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------
\begin{document}
\begin{centering}
  Application Narrative for DE-FOA-0001281\\
  \textbf{\large Error and Uncertainty Propagation for Fuel Cycle Calculations}\\
  2016 CFA Benefits of Collaboration 10565\\
\end{centering}
\vspace{1em}

\noindent\textbf{Technical Workscope Identifier:} FC-5.1b\\
\textbf{Principal Investigator:} Paul P.H. Wilson, Professor, University of Wisconsin-Madison\\
\textbf{Co-PI:} Dr. Baptiste Mouginot, University of Wisconsin-Madison\\
\textbf{Time Frame:} 3 years\\

Dr.\ Paul Wilson received his Dr.-Ing. from the Technical University of
Karlsruhe, Germany, in 1998, and his PhD from the University of
Wisconsin-Madison in 1999. He joined the Engineering Physics
Department in 2001 and founded the Computational Nuclear Engineering
Research Group (CNERG) where he directs research that delivers novel
analysis capability for nuclear systems. In addition to leading the
effort to develop CAD-based neutronics analysis capability across
application areas, he has been involved in various aspects of nuclear
fuel cycle analysis. Most recently, Dr. Wilson was the principal
investigator in an NEUP project to develop the next generation fuel
cycle simulator, Cyclus, that is at the foundation of this proposal.
Prior to that, Dr.\ Wilson led a NERI project to investigate the
economic impacts of repository benefits due to recycling spent nuclear
fuel.  Some models from this work were incorporated into the VISION
fuel cycle simulator and investigated for the DANESS fuel cycle
simulator.  This was followed by leading the development of GENIUSv2,
the fuel cycle simulator element of the SINEMA effort funded by Idaho
National Laboratory and Argonne National Laboratory.  Dr. Wilson was a
consultant for the Blue Ribbon Commission on America’s Nuclear Future
on the area of fuel cycle systems analysis and fuel cycle simulators.

Dr.\ Baptiste Mouginot received his PhD from the University of Paris
Sud-XI in 2011. During his PhD, he studied nuclear structure and
participated in research of the Giant Pairing Vibration, a collective
excitation state predicted by many theoretical models but never
observed and to half-life measurement in the Zn-74. He joined the
Experimental Research on Data Reactors and Energy (ERDRE) group of
Subatech Laboratory (CNRS/IN2P3, University of Nantes, Ecoles des
Mines de Nantes) in 2012 as a postdoc, then as a research
scientist. He was involved in the study on Accelerator Driven
System. Those results were included in the report given by the
Commissariat à l’énergie atomique (CEA) to the French parliament in
2012. He started and led the development of a fuel cycle tool for the
CNRS, called CLASS. He initiate the development of fuel fabrication
model and cross section predictor for the CLASS tool, and has been a
key developer of the polynomial regression and neural network methods
for fuel fabrication models in CLASS.  Dr. Mouginot joined the Cyclus
development team at UW-Madison in October 2015.


\label{LastPage}
\end{document}
