
\subsection{FCCI}

This goal is to establish a framework and collaboration/comparison tools for
defining comparison problems in a way that is agnostic to the particular NFCS
tool being testing and that facilitates comparison of the results in a
constructive and revealing manner.  This will be demonstrated by defining an
initial set of problems that any team can use to test their own NFCS tool and
gain a deeper understanding of the implications of different
development/modeling choices that are embedded in that tool. This will be
carried out in collaboration with the broader NFCS community. This will be used
as a showcase (through conferences contributions and scientific publications) to
promote the FCCI activities among the fuel cycle community. 


\subsubsection{Collaborative Framework for Problem Definition and Analysis} 

While it can be straightforward to define a problem for any single NFCS tool,
different modeling approaches and assumptions across a set of tools makes it
difficult to define those problems in a sufficiently generic manner.
Furthermore, the set of output data produced by each tool is different both in
the abstract (which data is generated) and the concrete (the format of that
data).  The success of an effort such as this lies in the ability for new
participants to easily access the problem definition and then also easily
compare their results to the previously generated and submitted results.

This task will focus on developing and formalizing the infrastructure needed for
effective collaboration, including a generalized ontology for defining canonical
problem inputs and outputs, mechanisms for proposing and refining new problem
definitions, submission of output data sets from a particular tool, and
web-based services to facilitate and automate the non-judgmental comparison of
the submitted outputs[3], all within an online community.  


\subsubsection{Problem definition} 

This task will be focused on the definition of new canonical problems that are
useful for demonstrating fundamental behavior of NFCS tools and/or highlighting
behaviors that distinguish different methodologies from each other.  A canonical
definition of the different problems and exercises should avoid any bias related
to the usage of a specific simulation tool and allow theoretically any tools
(with any conceptual design) to participate by simulating the same problem.  The
ontology developed above will help to accomplish this goal.  This will require
working with the FCCI collaboration to synthesize the different modeling
verification needs, and conceptualize problems that satisfy these needs while
allowing for deep analysis of potential differences due to modeling choices.
Experience from prior ad-hoc comparison efforts suggest that each problem’s
definition may require several updates based on the feedback of the different
analysts as their modeling progresses: reaching a canonical definition as an
asymptotic process. 


\subsubsection{Fuel Cycle Simulations and Analysis} 

This task will be dedicated to modeling the different problems of the FCCI, from
unit tests to the sensitivity analysis, using the Cyclus NFCS[2] developed at
the UW-Madison. The results of these simulations will be submitted, using the
infrastructure developed in Task 1, for analysis and comparison to submissions
generated using other NFCS tools.  These results will also, therefore, be
available to other participants as part of the comparison set for future
submissions.  The Cyclus framework includes multiple facility packages of
different fidelity levels, and the ability to swap individual facility models
within an otherwise constant fuel cycle scenario.  Thus, Cyclus can contribute
multiple submissions for each problem in the FCCI framework, each using a
different degree of fidelity.  Therefore, the FCCI framework will also serve as
a way to assess the impacts of these different fidelities with the Cyclus
ecosystem.  As new problems are identified and defined in Task 2, they will be
completed under this task.
